\cvsection{Publications \& Patent}
\begin{cvitems}
\item {\textbf{M. N. Sahadat}, N. Sebkhi, F. Kong, and M. Ghovanloo, “Standalone Assistive System to Employ Multiple Remaining Abilities in People with Tetraplegia,” in Biomedical Circuits and Systems Conference (BioCAS), 2018 IEEE, pp. 1–4, IEEE, 2018. (Accepted).}
\item {\textbf{M. N. Sahadat}, N. Sebkhi, and M. Ghovanloo, “Simultaneous Multimodal Access to Wheelchair and Computer for People with Tetraplegia,” in International Conference on Multimodal Interaction (ICMI), 2018 ACM, pp. 1–7, ACM, 2018. (Accepted).}
\item {\textbf{M. N. Sahadat}, A. Alreja, N. Mikail, and M. Ghovanloo, "Comparing the Use of Single Versus Multiple Combined Abilities in Conducting Complex Computer Tasks Hands-Free," in IEEE Transactions on Neural Systems and Rehabilitation Engineering, vol. 26, no. 9, pp. 1868-1877, Sept. 2018.}
\item {\textbf{M. N. Sahadat}, A. Alreja, and M. Ghovanloo, “Simultaneous multimodal PC access for people with disabilities by integrating head tracking, speech recognition,  and tongue motion,”IEEE  Transactions  on  Biomedical  Circuits and Systems, vol. 12, pp. 192–201, Feb 2018.}
\item {\textbf{M. N. Sahadat}  and  M.  Ghovanloo,  “Efficacy  assessment  of  multimodal tongue drive system (mTDS) in comparison to keyboard and mouse (KnM),”Archives of Physical Medicine and Rehabilitation, vol. 98, no. 12, pp. e163–e164, 2017.}
\item { M. Ghovanloo, \textbf{M. N. Sahadat}, Z. Zhang, F. Kong, and N. Sebkhi, “Tapping into tongue motion to substitute or augment upper limbs,” in Micro and  Nanotechnology  Sensors,  Systems,  and  Applications  IX,  vol.  10194,p. 1019413, International Society for Optics and Photonics, 2017.}
\item {\textbf{M. N. Sahadat},  A. Alreja,  P. Srikrishnan,  and M. Ghovanloo,  “A multimodal human computer interface combining head movement,  speech and tongue motion for people with severe disabilities,” in Biomedical Circuits and Systems Conference (BioCAS), 2015 IEEE, pp. 1–4, IEEE, 2015.}
\item{\textbf{M. N. Sahadat}, Z. Zhang, A. Alreja, P. Srikrishnan, S. Ostadabbas, N. Sebkhi,  and  M.  Ghovanloo,  “Live  demonstration:  A  tongue-operated  multimodal human computer interface and robotic rehabilitation system,” in Biomedical Circuits and Systems Conference (BioCAS), 2015 IEEE, pp. 1–1, IEEE, 2015.}
\item{Z. Zhang, S. Ostadabbas, \textbf{M. N. Sahadat}, N. Sebkhi, D. Wu, A. Butler, and M. Ghovanloo, “Enhancements of a tongue-operated robotic rehabilitation system,” in Biomedical  Circuits  and  Systems  Conference  (BioCAS),  2015 IEEE, pp. 1–4, IEEE, 2015.}
\item{A. Jafari, N. Buswell, A. Page, T. Mohsenin, \textbf{M. N. Sahadat}, and M. Gho-vanloo,  “Live demonstration:  Towards an ultra low power on-board processor for tongue drive system,” in Biomedical Circuits and Systems Conference (BioCAS), 2015 IEEE, pp. 1–1, IEEE, 2015.}
\item{B. I. Morshed, \textbf{M. N. Sahadat}, and S. Consul-pacareu, “Patterned carbon nanotube electrode,” Dec. 24 2015.  US Patent App. 14/725,885.}
\item{\textbf{M. N. Sahadat}, E. L. Jacobs, and B. I. Morshed, “Hardware efficient robust biometric identification from 0.58 second template and 12 features of limb(Lead  I)  ECG  signal  using  logistic  regression  classifier,”  in Engineering  in Medicine  and  Biology  Society  (EMBC),  2014  36th  Annual  International Conference of the IEEE, pp. 1440–1443, IEEE, 2014.}
\item{A. Mohapatra, \textbf{M. N. Sahadat}, B. I. Morshed, G. McGraw, A. P. Hoban,J.  A.  Jenning,  W.  O.  Haggard,  J.  D.  Bumgardner,  and  S.  R.  Mishra,“Stimuli-controlled  drug  delivery system  development  with  implantable biocompatible chitosan microbeads,” in IAJC-ISAM International Conference, 2014.}
\item{S. Consul-Pacareu, R. Mahajan, \textbf{M. N. Sahadat}, and B. I. Morshed, “Wearable ambulatory 2-channel EEG NeuroMonitor platform for real-life engagement monitoring based on brain activities at the pre-frontal cortex,” in 4th IAJC/ISAM Joint Intl. Conf., FL, p. 78, 2014.}
\item{ \textbf{M. N. Sahadat}, A. P. Hoban, B. I. Morshed, and W. O. Haggard, “Investigation of electrical stimulus on chitosan film based DDS,” in Engineering in Medicine and Biology Society (EMBC), 2014 36th Annual International Conference of the IEEE, pp. 1424–1427, IEEE, 2014.}
\item{R.  Mahajan,  S.  Consul-Pacareu,  M.  Abusaud,  \textbf{M. N. Sahadat},  and  B.  I. Morshed, “Ambulatory EEG NeuroMonitor platform for engagement studies of children with development delays,” in Smart Biomedical and Physiological  Sensor  Technology  X, vol. 8719,  p. 87190L, International Society for Optics and Photonics, 2013.}
\item{\textbf{M. N. Sahadat},  S.  Consul-Pacareu,  and  B.  I.  Morshed,  “Wireless  ambulatory ECG signal capture for HRV and cognitive load study using the NeuroMonitor platform,” in Neural Engineering (NER), 2013 6th International IEEE/EMBS Conference on, pp. 497–500, IEEE, 2013.}
\item{\textbf{M. N. Sahadat}, S. Hossain, A. Rahman, and S. T. Atique, “Power quality improvement of large power system using a conventional method,” Engineering, vol. 3, no. 08, p. 823, 2011.}
\item{ \textbf{M. N. Sahadat}, N. Al Masood, M. S. Hossain, G. Rashid, and A. H. Chowdhury, “Real power transfer capability enhancement of transmission lines using SVC,” in Power  and  Energy  Engineering  Conference  (APPEEC),  2011 Asia-Pacific, pp. 1–4, IEEE, 2011.}
\item{\textbf{M. N. Sahadat},  S.  Deeba,  S.  Ahmad,  G.  Biswas,  A.  Elahi,  N.  Zakaria,et al., “Reliability evaluation of Bangladesh power system using cumulant method,”  in Electronics  Computer  Technology  (ICECT),  2011  3rd  Inter-national Conference On, vol. 2, pp. 127–131, IEEE, 2011.}
\end{cvitems}